Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by XXXXXXX research grants.}

### 2015-10-19 latex/article.tex
figs

In this section, we detail the adaptive isosurface extraction
algorithm. The proposed approach is based on an octree representation
of the volumetric object on which an efficient adaptive triangulation
of the isosurface is constructed on GPU. Such approach is motivated by
the fact that the hierarchical representation of the object allows us
to handle large datasets and to locally adapt the level of details
with respect to the geometry or camera position. We first present the
octree representation and then the isosurface extraction from
hierarchical octree cells.

@@

\begin{figure}
  \begin{center}
    \subfigure{}{\includegraphics[height=0.17\textheight]{figs/partitioning}}
    \subfigure{}{\includegraphics[height=0.17\textheight]{figs/quadtree_activefront}}
  \end{center}
\caption{In \cite{dupuy2014quadtrees}, a linear quadtree is used to
  maintain a 2D hierarchical partitioning of space.  (Left) presents
  such a partitioning.  A cell is more or less subdivided depending on
  its distance to the camera.  They are also encoded with morton code,
  that identifies each cell with its position relatively to its
  parent.  (Right) shows the corresponding active front in the full
  tree.  This partition is entirely represented by storing the list of
  codes of the gray cells. }
\label{fig_quadtree_partitionning}
\end{figure}

>>>>

In this section, we detail the adaptive isosurface extraction
algorithm. The proposed approach is based on an octree representation
of the domain and object on which an efficient adaptive triangulation
of the isosurface is constructed on GPU. Such approach is motivated by
the fact that the hierarchical representation of the object allows us
to handle large datasets and to locally adapt the level of details
with respect to the geometry or camera position. We first present the
octree representation and then the isosurface extraction from
hierarchical octree cells.

@@

\begin{figure}
  \begin{center}
    \subfigure{}{\includegraphics[width=\textwidth]{figs/morton}}
    %%\subfigure{}{\includegraphics[height=0.17\textheight]{figs/partitioning}}
    %%\subfigure{}{\includegraphics[height=0.17\textheight]{figs/quadtree_activefront}}
  \end{center}
\caption{Morton codes associated to cells of a linear quatree. Each
  children cell morton code is obtained by adding a suffix to its
  parent code \emph{(left)}. The adpative representation consists of
  quadtree cells whose depth is view point dependent \emph{(right)}.}
\label{fig_quadtree_partitionning}
\end{figure}
